\documentclass[a4paper,10pt]{article}

% ==================== PACKAGES ====================
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\input{glyphtounicode}
\pdfgentounicode=1
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}

% ==================== PAGE LAYOUT ====================
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\geometry{
  left=1.2cm,
  top=0.5cm,
  right=1.2cm,
  bottom=0.7cm
}

% ==================== SECTION STYLE ====================
\titleformat{\section}
{\scshape\raggedright\normalsize}
{}{0em}{}[\titlerule]

\titlespacing*{\section}{0pt}{6pt}{3pt}

% ==================== CUSTOM COMMANDS ====================
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=0.4mm, topsep=0.4mm]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-1mm}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=0.4mm, topsep=0.3mm, parsep=0mm, partopsep=0mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0.5mm}}

\newcommand{\resumeProject}[4]{
  \item \textbf{#1} \hspace{0.4em} {\small #2} \\
  \begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textit{#3} & \textit{#4}
  \end{tabular*}
  \vspace{-4mm}
}

\newcommand{\icon}[1]{\raisebox{-0.1em}{\large #1}}

% ==================== DOCUMENT ====================
\begin{document}
\fontfamily{lmr}\selectfont
\small

% ==================== HEADER ====================
\begin{center}
    {\large\textbf{Mohammad Ninad Mahmud Nobo}} \\
    \vspace{1pt}
    {\textbf{Bangladesh University of Engineering and Technology (BUET) | CSE}} \\
    \vspace{3pt}
    \small
    \faEnvelope\ \href{mailto:mninadmnobo@gmail.com}{mninadmnobo@gmail.com} \quad
    \faGithub\ \href{https://github.com/mninadmnobo}{github.com/mninadmnobo} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/mninadmnobo}{linkedin.com/in/mninadmnobo} \\
    \faGlobe\ \href{https://mninadmnobo.github.io}{Portfolio (mninadmnobo.github.io)} \quad
    \faGraduationCap\ \href{https://scholar.google.com/citations?user=y5-A2oAAAAAJ&hl=en&oi=ao}{Google Scholar (M Ninad M Nobo)} \quad
    \faPhone\ +8801939444451
\end{center}

% ==================== SUMMARY ====================
\section{Summary}
CSE undergraduate at BUET focused on building intelligent systems at the intersection of large language models, software automation, and applied machine learning systems. Hands-on experience designing end-to-end AI-driven systems across mobile and backend platforms, with strong emphasis on reliability, scalability, and real-world deployment. Actively engaged in research on LLM-based software testing and medical AI, including dataset creation, evaluation pipelines, and trust-aware decision systems.

% ==================== EDUCATION ====================
\section{Education}

\textbf{Bangladesh University of Engineering and Technology (BUET)} \hfill \textbf{2022 -- Present} \\
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
Bachelor of Science in Computer Science and Engineering (CSE) & \textbf{CGPA: 3.61 / 4.00}
\end{tabular*}
\textbf{Relevant Coursework:} Data Structures and Algorithms, Digital Logic Design, Database Systems, Operating Systems, Computer Architecture, Computer Networks, Computer Graphics, Algorithm Engineering, Artificial Intelligence, Machine Learning \\
\textbf{Research Interests:} LLM Systems, Software Testing Automation, Applied Machine Learning, Medical AI

% ==================== RESEARCH EXPERIENCE ====================
\section{Research Experience}

\resumeSubHeadingListStart

\resumeProject
{Undergraduate Thesis: Web Testing Using Large Language Models}
{[ \href{https://github.com/mninadmnobo/Test-Case-Generator}{GitHub} ]}
{Python • LLMs • Web Automation • Prompt Engineering}
{2025 -- Present}
\resumeItemListStart
\item Designing LLM-based pipelines for automated web test generation using prompt-driven and programmatic approaches.
\item Creating and curating a dataset of functional descriptions and corresponding test cases for supervised evaluation.
\item Investigating coverage improvement and robustness of generated tests.
\resumeItemListEnd

\resumeProject
{MedCAR: Conflict-Aware Medical Reasoning System (Under Review)}
{[ \href{https://github.com/mninadmnobo/MedCAR}{GitHub} ]}
{Python • Deep Learning • Medical AI}
{2026 -- Present}
\resumeItemListStart
\item Built a multi-model system for chest X-ray analysis integrating heterogeneous AI tools.
\item Developed a conflict resolution pipeline to reconcile contradictory outputs using semantic reasoning and confidence calibration.
\item Designed trust-aware decision framework with uncertainty-based abstention for reliable predictions.
\resumeItemListEnd

\resumeProject
{Bengali-Loop: Community Benchmarks for Long-Form Bangla ASR and Speaker Diarization}
{[ \href{https://arxiv.org/abs/2602.14291}{arXiv: 2602.14291} ]}
{Python • Speech Processing • Machine Learning}
{2026}
\resumeItemListStart
\item Contributed to building a large-scale benchmark dataset for long-form Bangla ASR and speaker diarization in a multi-institution collaboration, developing data collection and annotation pipelines for real-world speech data.
\item Designed subtitle extraction and annotation workflows enabling evaluation with WER and DER.
\resumeItemListEnd

\resumeSubHeadingListEnd

% ==================== PROJECTS ====================
\section{Projects}

\resumeSubHeadingListStart

\resumeProject
{MindTrace: AI-Powered Dementia Care Application}
{[ \href{https://github.com/mninadmnobo/MindTrace}{GitHub} \textbar\
\href{https://www.youtube.com/watch?v=BpRmKZYAOhM}{Feature} \textbar\
\href{https://www.youtube.com/watch?v=i0GG_g0eZck}{Infrastructure} ]}
{Kotlin • Spring Boot • Spring AI • PostgreSQL • Redis • Firebase • Docker • Azure}
{2025}
\resumeItemListStart
\item Engineered an AI-driven mobile–backend system for dementia care with an Android frontend and scalable Spring Boot architecture, enabling real-time caregiver workflows and seamless system integration.
\item Designed accessibility-first UI/UX for cognitively impaired users, focusing on clarity, simplified interactions, and usability to enhance engagement and reduce cognitive load.
\resumeItemListEnd

\resumeProject
{Gemma VetCare: AI-Assisted Farming Support System}
{[ \href{https://github.com/mninadmnobo/GemmaVetCare}{GitHub} \textbar\
\href{https://www.youtube.com/watch?v=EoxyudCIVSo}{Feature} ]}
{Kotlin • Android Studio • Spring Boot • Spring AI • MongoDB}
{2025}
\resumeItemListStart
\item Built an AI-assisted Android application for veterinary decision support, integrating backend services to deliver real-time recommendations for diagnosis and treatment workflows.
\item Designed RESTful APIs optimized for low-connectivity environments with efficient request handling and streamlined data flow.
\resumeItemListEnd

\resumeProject
{Compiler Construction (Flex, Bison, 8086 Codegen)}
{[ \href{https://github.com/mninadmnobo/CompilerSessional}{GitHub} ]}
{C++17 • Flex • Bison/Yacc • Linux}
{2024}
\resumeItemListStart
\item Designed and implemented a full compiler pipeline for a C-like language, encompassing lexical analysis, parsing, semantic analysis, and intermediate code generation.
\item Generated optimized 8086 assembly code with symbol table management and basic optimizations.
\resumeItemListEnd

\resumeProject
{Computer Graphics Pipeline Implementation}
{[ \href{https://github.com/mninadmnobo/Computer-Graphics-Pipeline}{GitHub} ]}
{C++17 • OpenGL/GLUT • Rasterization • Ray Tracing}
{2025}
\resumeItemListStart
\item Implemented a complete graphics pipeline including transformations, clipping, rasterization with Z-buffering, and ray tracing.
\item Developed OpenGL-based rendering demos with camera systems supporting 6-DOF control and real-time interaction.
\resumeItemListEnd

\resumeSubHeadingListEnd

% ==================== TECHNICAL SKILLS ====================
\section{Technical Skills}
\textbf{Languages:} C/C++, Python, Java, Kotlin, JavaScript, SQL \\
\textbf{Backend:} Spring Boot, Spring AI, Node.js, Express.js, REST APIs \\
\textbf{AI/ML:} PyTorch, TensorFlow, Scikit-learn, LLM Systems \\
\textbf{Databases:} PostgreSQL, MongoDB, Redis \\
\textbf{Tools:} Linux, Git, Docker, Firebase

% ==================== ADDITIONAL INFORMATION ====================
\section{Additional Information}

\textbf{Spoken Languages:} Bangla (Native), English (Fluent), Hindi \& Urdu (Conversational), Arabic (Reading)

\noindent\textbf{Programming Profiles:} 
\hspace{1em}
\href{https://neetcode.io/profile/mninadmnobo}{NeetCode: mninadmnobo}
\hspace{1em}
\href{https://leetcode.com/u/mninadmnobo}{LeetCode: mninadmnobo}

\end{document}
